---
title: "Morrigan Hughes Cover Letter"
author: "Morrigan Hughes"
date: 'r Sys.Date()'
output: 
  pdf_document:
    latex_engine: lualatex
header-includes:
  - \input{preamble_coverletter.tex}
urlcolor: black
params:
  orgname:  "" # Organization name
  orgaddr:  "" # Organization address
  orgcity:  "" # Organization city, state, and zip
  mgrname:  "" # Full name of hiring manager, if known. Leave blank if not.
  mgrtitle: "" # Full title of hiring manager, if known. Leave blank if not.
  mgrtitls: "" # Short title of hiring manager [e.g. 'Senior Officer' instead of 'Senior Officer of Finance and Operations']
  postitle: "" # Position applying for
  
---
```{r setup-chunk, include=FALSE}
## Knitr Chunk Options
# Add number lines to source code blocks
knitr::opts_hooks$set(
  numberLines = function(options) {
    attrs <- paste0("attr.", options$numberLines)
    options[attrs] <- lapply(options[attrs], c, ".numberLines")
    options
  }
)

# Rest of the knitr chunk options
knitr::opts_chunk$set(
  numberLines = "source",
  echo = FALSE,
  fig.align = "center",
  dev = "png",
  dpi = 300
)

# Load RData with contact information
load("contact.RData")

# Load required packages
library(knitr)
library(kableExtra)
library(dplyr)
library(stringr)
```
```{r params-adjustments}
# If the hiring manager's name isn't known, change to 'Hiring Manager'
mgrname <- ifelse(params$mgrname == "", "Hiring Manager", params$mgrname)

# Create the dear/to line
dearline <- 
  paste(
    "Dear",
    case_when(
      params$mgrtitls == "" ~ "",
      TRUE ~ params$mgrtitls
    ),
    case_when(
      mgrname == "Hiring Manager" ~ mgrname,
      TRUE ~ str_extract(params$mgrname, "[[:alpha:]]{1,}$")
    )
  )
```
```{r req-exp-match}
##'* IMPORTANT *
##'* Remove this chunk if you want a more narrative cover letter than a direct comparison of requirements to experience *
##'* IMPORTANT *

# Create the requirements vs. experience tibble
experience <- tibble(
  # Enter the requirements from the job posting here
  requirement = c(
    "requirement 1",
    "requirement 2",
    "requirement 3"
  ),
  # Enter how experience matches those requirements here
  experience  = c(
    "matching experience 1",
    "matching experience 2",
    "matching experience 3"
  )
)

# Transform the tibble into a kable
experience_kable <- experience %>% 
  rename(
    'Your Requirements' = requirement,
    'My Experience'     = experience
  ) %>% 
  kable(
    format = "latex",
    booktabs = TRUE,
    align = "ll",
    linesep = "",
    escape = FALSE
  ) %>% 
  kable_styling(
    font_size = 8.5,
    stripe_color = "mgmhwine!10",
    latex_options = c("HOLD_position", "striped")
  ) %>% 
  row_spec(row = 0, color = "#591f63", align = "c")
```
\small
Morrigan G.M. Hughes \newline
`r phone` \newline
`r email` \newline

\vspace{10pt}
`r format(Sys.Date(), "%d %B, %Y")`
\vspace{10pt}

`r mgrname` \newline
`r params$mgrtitle` \newline
`r params$orgname` \newline
`r params$orgaddr` \newline
`r params$orgcity` \newline\vspace{10pt}

`r dearline`,

My name is Morrigan Hughes, and I'm writing to you today to apply for the open `r params$postitle` position with `r params$orgname`. With over 15 years experience in data analytics, data science, and quantitative and qualitative research methodologies, as well as more than 5 years experience directly leading and managing teams of skilled professionals, I believe I would be an excellent fit as your new `r params$postitle`. 

<!-- Comment out the below line if you want a more narrative cover letter -->
`r experience_kable`
<!-- write the rest of the cover letter below -->